Naturalness and Long-lived Beyond the Standard Model Particles

### 2017-07-25 tex/draft.tex
Start What is Natural SUSY? draft

\singlespacing

\maketitle

@@

\newpage
\tableofcontents
\newpage
\doublespacing
\linenumbers

@@

\section{Experimental Viability of Natural BSM}
\subsection{Limits Summary}
\subsection{What makes a SUSY model natural?}

>>>>

\pagenumbering{gobble}
\singlespacing
\maketitle

@@

\newpage
\tableofcontents
\newpage
\doublespacing
\linenumbers
\pagenumbering{arabic}

@@

\section{Experimental Viability of Natural SUSY}
    \fxnote{Comparison of 'Cornering', 'Toward Full', and 'What is' should do the trick} 
    \fxnote{Then add in current overall limits and reference specific LLP limits} 
    Cornering perspective
        When building a natural SUSY model, certain constraints are nearly unavoidable\fxnote{Dangerous. What if Linda knows how to avoid them?}. Specifically, the higgsino, which affects mH at tree level; the stop, which affects mH at one loop; and the gluino, which affets mStop at one loop and therefore mH at two, must all be heavy enough to pull mH up to 125 GeV\fxnote{Do I really understand this?} but light enough to avoid excessive fine tuning. Furthermore, the stop and gluino masses are correlated: a large mass difference between the two would constitute a new fine-tuning problem.

        Natural SUSY scenarios, then, are most likely to be constrained by limits on stop and gluino masses due to the strong interaction of these two objects as opposed to the colorless Higgsino\fxnote{Dear lord, I don't understand why I can't figure out how to word this sentence}. Indeed, limits on mStop and mGluino wipe out much of the natural parameter space for many models with decoupled first and second geration fermions, baryonic RPV, or compressed spectra that minimize missing energy while the MSSM is completely excluded.\fxnote{Define naturalness quantitatively here?}  \fxnote{Good spot for sweet Cornering plots}

        Demanding naturalness also constrains the messenger scale of SUSY breaking\fxnote{Make sure I understand this. Messenger scale == breaking scale?}. Corrections to the Higgs mass from stops and gluinos depend of the messenger scale\fxnote{reference eqs}, so natural SUSY generally prefers a lower scale.

        Despite strong contraints, SUSY remains one of the least-tuned options for BSM naturalness\fxnote{Make sure I can explain this and make sure it isn't plagarized from Cornering}.\fxnote{Good place for Feng "how much tuning is acceptable? discussion}

    Toward Full perspective

    What is perspective
